Human Factors Influencing Visual Statistical Inference

### 2013-06-12 sociology_paper.tex
gene expression data reference updated

\subsubsection{Design for Location effect} The experiment was set up based on the gene expression data with two groups. The groups are defined based on the Genotype and Empty Vector (EV). For each of the of the Genotype, gene expression data were collected in presence or absence of iron sufficiency. Two hypothesis were of primary interest. The Genotype effect and the Genotype and iron sufficiency interaction effect.

@@

Each observer was shown three lineups. First lineups shown is a randomly selected Interaction lineup, one from randomly selected Genotype lineup. Finally a test lineup was shown to screen out unusual evaluation. The subjects were not aware which one is the test plot but it was informed in the starting of the task about having a test plot. The test plot was very easy and everyone should detect the data plot. The MTurk worker was paid based on whether he or she could correctly detect the data plot. But the data on test plot are excluded from the analysis.

>>>>

\subsubsection{Design for Location effect} The experiment was set up based on the gene expression data \citep{atwood:2013} with two groups. The groups are defined based on the Genotype and Empty Vector (EV). For each of the of the Genotype, gene expression data were collected in presence or absence of iron sufficiency. Two hypothesis were of primary interest. The Genotype main effect and the Genotype and iron sufficiency interaction effect.

@@

Each observer was shown three lineups. First lineup shown was a randomly selected Interaction lineup, the second one was from randomly selected Genotype lineup. Finally a test lineup was shown to screen out unusual evaluation. The subjects were not aware which one is the test plot but it was informed in the starting of the task about having a test plot. The test plot was very easy and everyone should detect the data plot. The MTurk worker was paid based on whether he or she could correctly detect the data plot. But the data on test plot are excluded from the analysis.
